Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-09-25 paper/main.tex
Add sentence about why string mutants are bad

 Another approach is to have LLMs generate mutants for a given program. We experiment with prompting GPT-4 to generate mutants for a simple Haskell TODO management program.
 \cref{lst:haskellmutants} shows the mutants that GPT-4 generates for this program (formatted as before ==> after). Notice that some of the mutants generated make sense, and 
 resemble bugs a developer might make (replacing 0 with 1 or using the wrong data type). However, GPT-4 also generates a surprisingly high number of equivalent mutants, generating 
 (essentially) equivalent strings for all logging output. One is unlikely to generate tests that can kill these mutants, unless checking the exact string contents of all 
 logging messages.

>>>>

 Another approach is to have LLMs generate mutants for a given program. We experiment with prompting GPT-4 to generate mutants for a simple Haskell TODO management program.
 \cref{lst:haskellmutants} shows the mutants that GPT-4 generates for this program (formatted as before ==> after). Notice that some of the mutants generated make sense, and 
 resemble bugs a developer might make (replacing 0 with 1 or using the wrong data type). However, GPT-4 also generates equivalent mutants too, generating 
 (essentially) equivalent strings for all output to console. One is unlikely to generate tests that can kill these mutants, unless checking the exact string contents of all 
 logging messages. The error messages (potentially) could be checked, but the semantically equivalent meaning of these strings makes them poor mutants.
